Enhancement of SDR in Thessaloniki

### 2023-11-24 GHI_enh_03_process.tex
Commit 2023-11-24 22:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-21}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/unnamed-chunk-6-1} \end{center}

\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
\subsection{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/strong_days-30} \end{center}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchtrendyear-1}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/unnamed-chunk-9-1} \end{center}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchtrendday-1}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/enchNtrendday-1}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_02_process_files/figure-latex/szacases-1}

@@

\begin{verbatim}
2023-11-21 10:00:59.8 athan@sagan GHI_enh_02_process.R 0.429637 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2023-11-24}

@@

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchtrendyear-1}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-7-1} \end{center}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchtrendday-1}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/enchNtrendday-1}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/szacases-1}

@@

\begin{verbatim}
2023-11-24 16:31:40.1 athan@tyler GHI_enh_03_process.R 0.225677 mins
\end{verbatim}
